Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-29 journal/article.tex
Work in progress

Work in progress...

Top down

Bottom up

Big bang

Transitional

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.61\textwidth}
                     >{\raggedright\arraybackslash}p{0.31\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Pilot programs and other piloting   & 
                P6, P7, P8, P9, P10, P11, P14, P16, P18, P22, P23, P24,
                P27, P29, P36, P38, P40, P41, P43, P45, P46, P47  \\
        \bottomrule
    \end{tabular}
    \caption{Activities in the organization aiming to create change}
    \label{table:transformation_activities}
\end{table}

@@

Reasons for piloting

@@

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.42\textwidth}
                     >{\raggedright\arraybackslash}p{0.50\textwidth} }
        Investment for transformation      &  Described in  \\
        \midrule
        Agile project management tools  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Continuous builds and testing  &
                P5, P11, P16, P17, P25, P27, P34, P39, P42, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Investments aiming to make agile methods perform better}
    \label{table:transformation_investments}
\end{table}

>>>>

* Top down

* Bottom up

* Big bang

* Step wise

* Transformation is continuous, hard work, and takes time

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Pilot programs and other piloting   & 
                P6-P11, P14, P16, P18, P22, P23, P24, P27, P29,
                P36, P38, P40, P41, P43, P45, P46, P47  \\  %22
        \bottomrule
    \end{tabular}
    \caption{Summary of activities aiming to advance the transformation}
    \label{table:transformation_activities}
\end{table}

@@

Reasons for piloting?

Did it work?

@@

% Training

Who?

Why?

Who teaches?

Did it work?

As the organization is changing it is necessary that people know what to change
into. Therefore the majority of cases described the use of training in the
transformation.

It was very common that the first persons involved with agile received
training. In the start change leaders and pilot teams attended firmal training
on agile development.

Management was also among the first ones to receive agile training, and they
received more in-depth training than the rest of the organization [P11].

The type of training that was offered to teams was typically only a single
introductory session [P16, P20], although some organizations invested in a
multi-day course [P19].

Training was reported to make a difference between success and failure of teams
[P6].
It became clear that training was necessary to retain an agile culture [P19].

The training curriculum was evolving as trainers improved and learned the needs
of the organization [P6]. In some cases training workshops was even initially
tailored to suite the needs of the project [P23].

Typically the training started with sending management and possibly a pilot team
to in-depth training. After the pilot other teams started transitioning to the
new development model. Teams about to transition typically attended a shorter
agile introduction session, lasting for one day or less. The reason for reduced
training for development teams was that there were many people to be trained.
The lack of training for teams was compensated with coaching during ongoing
projects.

Training management served the purpose of creating a unified understanding of
the methods at top level [P11, P24].

It was common that the first introductory events were held by known industry
experts [P25, P27].

Some training included simulation workshops [P40, P41].
Hands-on workshops [P46].

[P3]
* Who: The change leader
* When: Before starting with the transformation
* What: CSM course
* Teacher: Ken Schwaber, later the change leader
* Works: Education in itself increased interest in agile
* Particular: The insight increased less than anticipated for anyone taking the course

[P6]
* When: initial thing
* Who: The pilot team
* What: Comprehensive training, CSM course
--
* When: Later
* Who: Everyone
* What: The training curriculum was evolving as trainers improved and learned the needs of the organization
* Works: There was a difference between success and failure
* Particular: They have invested and investigated what training suits best

[P8]
* When: Pilot teams reported trouble
* Who: Pilot teams
* Particular: Training was increased when there was problems getting started in pilots

[P9]
* Who: Pilot teams
* Who: Also other interested people
* What: Multi-day comprehensive training
* Teacher: Experienced external agile coaches

[P11]
* Who: Management team
* When: At start of the transformation
* What: Common understanding of Scrum principles
--
* Who: Rest of the organization
* Teacher: Scrum masters
* What: Two hour overview -- enough understanding to get started
* What: The Scrum masters assisted the transformation of teams
* Particular: The Scrum masters were supposed to deepen the teams' understanding over time

[P16]
* When: First
* Who: Program and functional managers
* What: CSM course
--
* Who: Every team
* What: a short agile introduction session
* In depth training for PO and CSM roles

[P18]
* When: First
* Who: The pilot team
* Teacher: Agile consultant
* What: One day course, coaching wiith kick-off and initial planning

[P19]
* Teacher: Ken Schwaber
* When: Initially (?)
* Who: 60 Scrum masters
-- 
* When: Later
* Who: 240 employees
* What: 2 day course
* Why: It became clear that agile training was necessary to retain the culture.

[P20, 21]
* When: Initial
* Who 30 team members from different roles
* Works: There was too little training
* Particular: Failure was attributed partially to the lack of training

[P23]
* What: A full day deep dive program event
* Who: Projects could request this training
* What: Project specific training

[P24]
* Who: CEO, CTO, managers, high-ups
* What: Scrum master training, product owner training
* When: Initially
* What: Create a unified understanding
--
* Who: Both the main site and the offshore site
* Teacher: The CTO, internal certified Scrum trainers

[P25]
* When: During the first year
* When: Initially, by acclaimed experts
* Who: The personnel
* Teacher: Agile transformation team, managers, external consultants

[P27]
* Teachers: Renowed industry experts
* What: Educating specific XP practices
* Why: Help teams transition from waterfall to agile

[P30]
* Teacher: Jeff Sutherland
* Who: Most of the engineering group, several managers, executives

[P32]
* When: A series of education events
* Who: 100 persons at a time, 3000 in total
* What: Practice agile in workshops
* Particular: A productized training workshop

[P35]
* Who: The teams
* What: Training
* Particular: Product managers did not receive training, and they stuck in old ways

[P37]
* When: Four months after start
* Who: All developers
* Why: To build consensus, acceptance
* What: Two day training workshop, outside the daily project environment

[P39]
* When: First step
* Who: The development team
* Why: Team members shared same values, and used the same methods

[P40]
* When: Pilot projects
* Who: Several teams
* Teacher: Consultants
* What: Training, CSM training
* What: Simulation workshops

[P41]
* Who: All project teams
* Teachers: Transition team, external coaches
* What: full day workshop
* What: Simulation
* Particular: Mixing attending teams to create new relationships

[P43]
* Who: The rollout team
* What: Training, learning from consultants

[P44]
* Who: Entire development team
* What: Workshop on agile development and Scrum
* What: 15 CSM certifications
* Teacher: Ken Schwaber

[P45]
* When: Initial
* Who: Pilot teams
* What: Overview, one day training
* What: In-depth training for Scrum masters and POs
--
* When: After one year
* What: Mentor training for experienced agilists
--
* What: A one day lean training workshop, in the fashion of the earlier ones

[P46]
* Who: Everyone, developers and managers
* What: Scrum and agile training
* Teacher: Internal
--
* When: Pilot projects
* What: Key persons in pilot teams
* Teacher: Ken Schwaber
--
* What: A series of education events
* What: Introduction, a hands-on workshop (simulation?)

[P48]
* When: The first step
* Who: Everyone, 30 teams, project managers, 800 people in total
* Why: To understand where the organization is going, when shifting away from waterfall
* Particular: It took time, as there were so many people, but it was straight forward in the end

[P49]
* Teacher: Internal coaching team, external consultant
* What: A productized agile learning workshop
* What: 4 day event
* Who: Several teams
* Who: 30\% of teams got the workshop, others got nothing
* Works: The workshop was heavy, but it delivered results

[P50]
* Who: Product marketing, management
* What: product owner certification

[P51]
* Teacher: External consultant
* Why: Figure out how Scrum works
--
* Who: The company
* What: in-house training of how Scrum works
* Teacher: in-house

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.42\textwidth}
                     >{\raggedright\arraybackslash}p{0.50\textwidth} }
        Investment for transformation      &  Described in  \\
        \midrule
        Agile project management tools  &
                P10, P11, P14, P16, P17, P26, P33,
                P41, P43, P44, P45, P48, P50 \\
        Continuous builds and testing  &
                P5, P11, P16, P17, P25, P27, P34, P39, P42, P50 \\
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P32, P45  \\
        Refurbishing work areas and other spaces   &
                P6, P22, P35, P36, P38, P42, P46, P48 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investments aiming to make agile methods perform better}
    \label{table:transformation_investments}
\end{table}
